Quantile Forecast Matching with a Bayesian Quantile Gaussian Process Model

### 2025-08-19 quantile_matching.tex
small .tex update
fix bib

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,scrextend,mathtools}
\usepackage{hyperref}
% \usepackage{newtxmath} %for making indicator function
% \RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,backref=page,backref=page]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

@@

%% Abstract
\begin{abstract}
A set of probabilities along with corresponding quantiles are often used to 
define predictive distributions or probabilistic forecasts. These quantile 
predictions offer easily interpreted uncertainty of an event, 
and quantiles are generally straightforward to estimate using standard 
statistical and machine learning methods. However, compared to a distribution 
defined by a probability density or cumulative distribution function, a set of 
quantiles has less distributional information. When given estimated 
quantiles it may be desirable to estimate a fully defined continuous 
distribution function, and many researchers do so to make evaluation or 
ensemble modeling simpler. Most existing methods for fitting a distribution to 
quantiles lack accurate representation of the inherent uncertainty from 
quantile estimation or are limited in their applications. In this manuscript we 
present a Gaussian process model, the quantile Gaussian process, which is based 
on established theory of quantile functions and sample quantiles, to construct 
a probability distribution given estimated quantiles. A Bayesian application of 
the quantile Gaussian process is evaluated for parameter inference, and 
distribution approximation in simulation studies and the quantile Gaussian 
process is used to approximate the distributions of quantile forecasts from the 
2023-24 US Centers for Disease Control collaborative flu forecasting 
initiative. The simulation studies and data analysis show that the quantile 
Gaussian process leads to accurate inference on model parameters, estimation of 
a continuous distribution, and uncertainty quantification of sample quantiles.
\end{abstract}

@@

The use of quantiles in statistical modeling and in reporting inferential or 
predictive uncertainty is widespread, and reporting several quantiles or 
predictive intervals is common for probabilistic forecasting 
\cite[]{gneiting2023model}. Quantiles can be easier to interpret than 
statistical model parameters and are often used to define confidence or 
prediction intervals. Thus with multiple quantiles for a particular outcome, 
one has a measure of uncertainty.
Estimating quantiles in the presence of covariates via 
quantile regression is a common
statistical and machine learning strategy, and where parametric models are 
complicated or nonexistent quantiles may be easier to estimate via machine 
learning methods \cite[]{martin2022direct,chung2021beyond, koenker2017quantile, 
koenker1978regression}. In estimating multiple quantiles, quantile regression 
often provides a tradeoff with parametric modeling in that for some problems 
quantile regression may be easier to perform but that predicted quantiles lack 
the detailed information of a fully defined predictive distribution 
\cite[]{pohle2020murphy}. 
% Quantile regression may also lead to other issues 
% such as quantile crossing where an estimated quantile may be smaller than 
% another estimated quantile with for a lower probability level 
% \cite[]{chernozhukov2010quantile,he1997quantile}.
% Data is often reported as quantiles, 
Perhaps, for data privacy reasons, data quantiles are often reported as 
summaries of the data.
% along with predictive distributions. 
% \jarad{Predictive distributions for what?}
Census or medical data, which can be very large or personal to the subjects, 
may be published as summary or aggregate data including percentiles (quantiles) 
and medians 
\cite[]{simpson2023interpolating,cdc2022growthcharts,nirwan2020bayesian}. In 
collaborative forecast initiatives and competitions, probabilistic forecasts 
are often submitted as a set of predictive quantiles 
% for given probabilities 
\cite[]{gneiting2023model,hong2016probabilistic}. In recent years disease 
outbreak forecast hubs require that all forecasts submitted by outside 
participants be represented by  several predictive intervals or quantiles. 
This standardized representation allows for straightforward forecast scoring 
and ensemble building 
\cite[]{mathis2024evaluation,mathis2023flusight,Cramer2022-hub-dataset,
cramer2022evaluation,sherratt2023predictive,bracher2021evaluating}.

A set of quantiles may provide distributional information for an event, but it 
is not as informative as a distribution defined by a cumulative distribution 
function (CDF), the inverse-CDF or quantile function QF, or a probability 
density/mass function (PDF), and quantiles provide no distribution tail 
information --information for values below the smallest quantile or above the 
largest quantile. Another drawback for using quantiles to define a distribution 
is that many tools for evaluating or scoring continuous distributions require 
a CDF or PDF
% \jarad{what does 'fully defined' mean?} 
\cite[]{gneiting2007strictly,gneiting2014probabilistic}. Likewise combining 
distributions into an ensemble distribution is commonly 
% \jarad{most often? perhaps use commonly}
done by aggregating multiple QFs or 
CDFs/PDFs, the latter being possible only when a CDF/PDF is available 
\cite[]{gneiting2005calibrated,wang2023forecast}.

@@

Besides the CDF, PDF, and QF a  fourth infrequently mentioned defining function 
of a continuous random variable is the quantile density function (QDF). As the 
PDF is the derivative of the CDF, the QDF $q:[0,1] \rightarrow \mathbb{R}$ is 
the derivative of the QF defined as
\[
    q(p) = \frac{dQ(p)}{dp}.
\]
If $Q(p)$ is the inverse of a CDF $F(x)$, a calculus result shows that the 
reciprocal QDF $[q(p)]^{-1} = f(Q(p))$, or the PDF evaluated at the QF 
evaluated at $p$ 
\cite[]{perepolkin2023tenets, gilchrist2000statistical}. The QDF is important 
for establishing the CLTs in section \ref{sec:samp_quants} and for the QGP 
models introduced in section \ref{sec:qgp_model}.

@@

The asymptotic distribution of a set of sample quantiles is given in 
(\ref{eq:qclt}), and it is the basis for the QGP model for QM in section 
\ref{sec:qgp_model}. For independent draws $Y_1, ..., Y_n$ from a continuous 
random variable with CDF $F$, PDF $f$, and QF $Q$, and with a set of sample 
quantiles calculated by (\ref{eq:quant_df}), theorem \ref{thm:qclt} holds. 
Note that in (\ref{eq:qclt}), $N_K(\cdot, \cdot)$ refers to a multivariate 
normal distribution with $K$ dimensions, and in (\ref{eq:qclt_covariance}) the 
operator $a \wedge b$ is the minimum of the values $a$ and $b$.

@@

\begin{equation}
    \label{eq:qclt}
    \sqrt{n}(\hat{\boldsymbol{Q}}_n(\boldsymbol{p}) - 
    \boldsymbol{Q}(\boldsymbol{p})) \overset{D}{\rightarrow} 
    N_K(0, \boldsymbol{\mathcal{K}})
\end{equation}
where $\boldsymbol{\mathcal{K}}$ is a $K\times K$ with the $ij^{th}$ 
entry $\kappa_{ij}$ where

\begin{equation}
    \label{eq:qclt_covariance}
    \kappa_{ij} = \frac{p_i \wedge p_j - p_i p_j}{f(Q(p_i)) f(Q(p_j))}
\end{equation}
\end{theorem}

@@

\begin{equation}
    \label{eq:qgp}
\hat{\boldsymbol{Q}}_n(\boldsymbol{p}) \sim N_K(\boldsymbol{Q}_{\theta}(\boldsymbol{p}), n^{-1} \boldsymbol{\mathcal{K}}_{\theta})
\end{equation}
Here $\theta$ is an unknown parameter to be estimated from the data. The 
covariance matrix $\boldsymbol{\mathcal{K}}_{\theta}$ has entries from the 
covariance function $\kappa_{\theta}(\cdot, \cdot)$ where 
\[
\kappa_{\theta}(p, p') = \frac{p\wedge p' - p p'}{f_{\theta}(Q_{\theta}(p)) f_{\theta}(Q_{\theta}(p'))}, \quad p, p' \in (0,1)
\]

@@

Take for instance the data 
$\boldsymbol{X} = \left(\textbf{1}, \Phi^{-1}(\boldsymbol{p})\right)$ and the 
parameter vector $\beta = (\mu, \sigma)$. Assuming the sample size $n$ is 
unknown and setting $\sigma^2/n = \gamma^2$, model (\ref{eq:norm_qgp}) then 
becomes
\[
    \hat{\boldsymbol{Q}}_n(\boldsymbol{p}) \sim N_K\left(X\beta, 
\gamma^2 \boldsymbol{\Psi}\right)
\]
In this model, one simplifying assumption may be to treat $\sigma$ and 
$\gamma^2$ separately and proceed to fit a standard linear regression model. 
All frequentist and Bayesian results of the linear regression model apply, 
including the existence of conditionally conjugate prior distributions. The 
positive constraint on $\sigma$ can also be dealt with without adding much 
complication (see \cite{gelman2013bayesian} pgs. 377-378). If for a certain 
problem it is important to make inference on the unknown $n$, or $\sigma$ and 
$\gamma^2$ cannot treated as separate, then one may estimate the two parameters 
by assigning appropriate prior distributions to $\sigma$ and $n$ and reverting 
back to (\ref{eq:norm_qgp}). In section \ref{sec:simulation_analyses}, we 
analyze a normal QGP in a simulation study where we assign independent prior 
distributions to $\sigma$ and $n$, and $\sigma$ is treated as both a regression 
coefficient and as part of the variance.

@@

We define a modified version of the WD, the uniform 1-WD (UWD1) in 
(\ref{eq:pit_wass_dist}). Here we take $F_X$ to be the CDF of a continuous 
random variable $X$. For a different continuous random variable $\xi$ with CDF 
$F_{\xi}$, $F_X(\xi)$ is a random variable with support on $[0,1]$. We let 
$F_{X,\xi}$ be the CDF of the random variable $F_X(\xi)$. Then the measure in 
(\ref{eq:pit_wass_dist}) is a measure of how close $F_X(\xi)$ is the the CDF of 
a standard uniform distribution, noting that by the PIT, if 
$\xi \overset{D}{=} X$, $F_X(\xi)$ is the random variable of a standard uniform 
distribution. Multiplying the integral in (\ref{eq:pit_wass_dist}) by two 
ensures the measure takes values between 0 and 1 \cite[]{645854} where a value 
near 0 means $\xi$ and $X$ are "near" each other.

@@

\subsubsection{Normal parameter estimation}
In this simulation study we fit the ORD and IND models to quantiles estimated 
from independent samples from a normal distribution and compare parameter 
estimation with fits from the QGP model. Quantiles were simulated by first 
drawing a sample of size $n$ from a known distribution then estimating $K$ 
quantiles given probabilities $\{p_1, ..., p_K\}$. The ORD, IND, and QGP models 
were then fit to the quantiles where $F$ was set to be the CDF of a normal 
distribution. For each of 
$n \in \{50, 150, 500, 1{,}000, 5{,}000\}$ and 
% $K \in \{3,7,15,50\}$
$K = 23$, there 
were 500 simulation replicates. The data were simulated from a normal 
distribution with mean $\mu = 4$ and standard deviation $\sigma = 3.5$.
For each of QGP, ORD, and IND models, we assigned the same prior distributions 
to $\mu$ and $\sigma$. When $n$ is unknown, we also assigned it a prior 
distribution. The prior distributions were $\mu \sim N(5,7^2)$, 
$\sigma \sim N(0, 6^2) \mathds{1} \{\sigma > 0\}$, and
$n \sim N(0,3000^2)\mathds{1}\{n > 0\}$.
% \begin{align*}
%     \mu &\sim N(5,7^2) \\
%     \sigma &\sim N(0, 6^2) \mathds{1}\{\sigma > 0\}\\
%     n &\sim N(0,3000^2)\mathds{1}\{n > 0\}.
% \end{align*}
For the IND model the prior on the independent parameter 
$\sigma_{\rho}\mathds{1}\{n > 0\}$ from model (\ref{eq:ind_quantile}) is 
$1/\sigma_{\rho} \sim N(0, 3000^2)$, which is similar to the prior on $n$ for 
the QGP and ORD models. For each fit, the HMC chain was run for 60,000 draws 
with the first 10,000 discarded as a burn-in.

@@

The top of figure \ref{fig:normal_cov_dists} shows the 90\% coverage of 
the posterior distribution credible intervals as $n$ increases for 
$\mu$, $\sigma$ and $n$ for five models. QGP-n and ORD-n models where $n$ is 
known are included along with QGP, ORD, and IND. 90\% credible intervals of the 
parameters were calculated by computing the $0.05^{th}$ and $0.95^{th}$ 
quantiles from the posterior distribution samples. The coverage percentage is 
calculated as the percentage of the 500 replicates which the true parameter 
value was within the 90\% credible interval.
As expected, the nominal coverage for the QGP and ORD models is better than 
that of the IND model, and for the two models where $n$ is known the coverage 
is better than where it is unknown, particularly for lower values of 
$n$ and $K$. The coverage for the ORD models appears to be slightly better 
than for the QGP models though not by much, and the difference
decrases as $n$ increases. 
The superior performance of the ORD model is possibly because it
provides exact inference 
whereas the QGP model provides asymptotic inference.

\begin{figure}[hbt!]
%\begin{subfigure}{.465\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/normal_coverage.png}
  % \caption{}
  % \label{MLEDdet}
%\end{subfigure}\hfill % <-- "\hfill"
%\begin{subfigure}{.524\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/normal_dists.png}
  \centering
  \includegraphics[width=1\linewidth]{Images/normal_cover_dist.png}
  % \caption{}
  % \label{energydetPSK}
%\end{subfigure}
\caption{Posterior coverage (top) for models of $K = 23$ quantiles
calculated as the percentage of times the 
true parameter fell within the modeled 90\% credible interval over the 500 
replications. Coverage is faceted by the normal parameters $\mu$, $\sigma$,
and shown by increasing sample size 
($x$-axis). The five models QGP, ORD, QGP-n, ORD-n, and IND are colored as 
shown the legend. The horizontal line (black) is at the nominal 90\% level. 
Only QGP and ORD appear for inference for the parameter $n$ as they are the 
only two models which 
estimate an unknown $n$.
Distance between the true distribution and the estimated QM predictive 
distribution (bottom) averaged over the 500 replications. Distances include the 
UWD1, TV, and KLD for by increasing sample 
size ($x$-axis).}
\label{fig:normal_cov_dists}
\end{figure}

@@

\begin{figure}[hbt!]
%\begin{subfigure}{.465\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/uk_cover50.png}
  % \caption{}
  % \label{MLEDdet}
%\end{subfigure}\hfill % <-- "\hfill"
%\begin{subfigure}{.532\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/uk_cover95.png}
  % \caption{}
  % \label{energydetPSK}
%\end{subfigure}
\centering
\includegraphics[width=.9\linewidth]{Images/uk_cover_dist.png}
\caption{
(top) Percent coverage of the true quantile values for select quantiles for 
500 simulated replicates of sample quantiles averaged over all $K = 23$
quantiles faceted by the true EV, La, and normal mixture distributions.
The plots shows percent coverage for the 95\% credible intervals. The models 
included are QGP, ORD, and IND. The vertical bar (black) shows the nominal 
coverage level.

(bottom) Distance between the true distribution and the QM estimated 
distribution 
averaged over 500 simulation replicates and measured by KLD, TV and UWD1. 
Plots are faceted by distribution with the distributions being 
EV, La, and MIX. 
Lines are colored and shaped by QM method, and are drawn by increasing sample 
size $n$.}
\label{fig:uk_cover}
\end{figure}

The bottom of \ref{fig:uk_cover} shows the UWD1, TV, and KLD distances between 
QM and true distributions averaged over 500 simulation replicates for the 
five QM methods. In the UWD1 plot, there appears to be little or no difference
in performance between the QGP, ORD, IND, and SPL fits, but each of these
outperforms the KDE fits. For TV, the QGP, ORD, and SPL perform similarly, 
though the QGP does the best for the MIX distribution.
And for KLD, the QGP and ORD perform the best for lower values of $n$, but as
$n$ increases, SPL appears to perform the best.

>>>>

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,scrextend,mathtools}
% \usepackage{hyperref}
% \usepackage{newtxmath} %for making indicator function
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\newcommand{\jarad}[1]{{\color{red} ?? Jarad: #1}}

@@

%% Abstract
\begin{abstract}
A set of probabilities along with corresponding quantiles are often used to 
define predictive distributions or probabilistic forecasts. These quantile 
predictions offer easily interpreted uncertainty of an event, 
and quantiles are generally straightforward to estimate using standard 
statistical and machine learning methods. However, compared to a distribution 
defined by a probability density or cumulative distribution function, a set of 
quantiles has less distributional information. When given estimated 
quantiles, it may be desirable to estimate a fully defined continuous 
distribution function. Many researchers do so to make evaluation or 
ensemble modeling simpler. Most existing methods for fitting a distribution to 
quantiles lack accurate representation of the inherent uncertainty from 
quantile estimation or are limited in their applications. In this manuscript, we 
present a Gaussian process model, the quantile Gaussian process, which is based 
on established theory of quantile functions and sample quantiles, to construct 
a probability distribution given estimated quantiles. A Bayesian application of 
the quantile Gaussian process is evaluated for parameter inference and 
distribution approximation in simulation studies. The quantile Gaussian 
process is used to approximate the distributions of quantile forecasts from the 
2023-24 US Centers for Disease Control collaborative flu forecasting 
initiative. The simulation studies and data analysis show that the quantile 
Gaussian process leads to accurate inference on model parameters, estimation of 
a continuous distribution, and uncertainty quantification of sample quantiles.
\end{abstract}

@@

The use of quantiles in statistical modeling and in reporting inferential or 
predictive uncertainty is widespread, and reporting several quantiles or 
predictive intervals is common for probabilistic forecasting 
\cite[]{gneiting2023model}. Quantiles can be easier to interpret than 
statistical model parameters and are often used to define confidence or 
prediction intervals. Thus with multiple quantiles for a particular outcome, 
one has a measure of uncertainty.
Estimating quantiles in the presence of covariates via 
quantile regression is a common
statistical and machine learning strategy, and where parametric models are 
complicated or nonexistent quantiles may be easier to estimate via machine 
learning methods \cite[]{martin2022direct,chung2021beyond, koenker2017quantile, 
koenker1978regression}. In estimating multiple quantiles, quantile regression 
often provides a tradeoff with parametric modeling in that for some problems 
quantile regression may be easier to perform but that predicted quantiles lack 
the detailed information of a fully defined predictive distribution 
\cite[]{pohle2020murphy}. 
% Quantile regression may also lead to other issues 
% such as quantile crossing where an estimated quantile may be smaller than 
% another estimated quantile with for a lower probability level 
% \cite[]{chernozhukov2010quantile,he1997quantile}.
% Data is often reported as quantiles, 
Perhaps, for data privacy reasons, data quantiles are often reported as 
summaries of the data.
% along with predictive distributions. 
% \jarad{Predictive distributions for what?}
Census or medical data, which can be very large or personal to the subjects, 
may be published as summary or aggregate data including percentiles (quantiles) 
and medians 
\cite[]{simpson2023interpolating,cdc2022growthcharts,nirwan2020bayesian}. In 
collaborative forecast initiatives and competitions, probabilistic forecasts 
are often submitted as a set of predictive quantiles 
% for given probabilities 
\cite[]{gneiting2023model,hong2016probabilistic}. In recent years, disease 
outbreak forecast hubs require that all forecasts submitted by outside 
participants be represented by  several predictive intervals or quantiles. 
This standardized representation allows for straightforward forecast scoring 
and ensemble building 
\cite[]{mathis2024evaluation,mathis2023flusight,Cramer2022-hub-dataset,
cramer2022evaluation,sherratt2023predictive,bracher2021evaluating}.

A set of quantiles may provide distributional information for an event, but it 
is not as informative as a distribution defined by a cumulative distribution 
function (CDF), the inverse-CDF or quantile function QF, or a probability 
density/mass function (PDF), and quantiles provide no distribution tail 
information --information for values below the smallest quantile or above the 
largest quantile. Another drawback for using quantiles to define a distribution 
is that many tools for evaluating or scoring continuous distributions require 
a CDF or PDF
\cite[]{gneiting2007strictly,gneiting2014probabilistic}. Likewise combining 
distributions into an ensemble distribution is commonly 
done by aggregating multiple QFs or 
CDFs/PDFs, the latter being possible only when a CDF/PDF is available 
\cite[]{gneiting2005calibrated,wang2023forecast}.

@@

Besides the CDF, PDF, and QF, a  fourth infrequently mentioned defining function 
of a continuous random variable is the quantile density function (QDF). As the 
PDF is the derivative of the CDF, the QDF $q:[0,1] \rightarrow \mathbb{R}$ is 
the derivative of the QF defined as
\[
    q(p) = \frac{dQ(p)}{dp}.
\]
If $Q(p)$ is the inverse of a CDF $F(x)$, a calculus result shows that the 
reciprocal QDF $[q(p)]^{-1} = f(Q(p))$, or the PDF evaluated at the QF 
evaluated at $p$ 
\cite[]{perepolkin2023tenets, gilchrist2000statistical}. The QDF is important 
for establishing the CLTs in section \ref{sec:samp_quants} and for the QGP 
models introduced in section \ref{sec:qgp_model}.

@@

The asymptotic distribution of a set of sample quantiles is given in 
(\ref{eq:qclt}), and it is the basis for the QGP model for QM in section 
\ref{sec:qgp_model}. For independent draws $Y_1, ..., Y_n$ from a continuous 
random variable with CDF $F$, PDF $f$, and QF $Q$, and with a set of sample 
quantiles calculated by (\ref{eq:quant_df}), theorem \ref{thm:qclt} holds. 
Note that in (\ref{eq:qclt}), $N_K(\cdot, \cdot)$ refers to a multivariate 
normal distribution with $K$ dimensions, 
\jarad{Include the mean and covariance matrix in this definition? I think we should.}
and in (\ref{eq:qclt_covariance}) the 
operator $a \wedge b$ is the minimum of the values $a$ and $b$.
\jarad{Do we need to be concerned about the order of operations when using $\wedge$? I believe $p_i \wedge p_j - p_i p_j = (p_i \wedge p_j) - p_i p_j$, but it could be $p_i \wedge p_j - p_i p_j = p_i \wedge (p_j - p_i p_j)$.
Using the $()$ would make it clear without having to define the order of operations.}

@@

\begin{equation}
    \label{eq:qclt}
    \sqrt{n}(\hat{\boldsymbol{Q}}_n(\boldsymbol{p}) - 
    \boldsymbol{Q}(\boldsymbol{p})) \overset{D}{\rightarrow} 
    N_K(0, \boldsymbol{\mathcal{K}})
\end{equation}
where $\boldsymbol{\mathcal{K}}$ is a $K\times K$ with the $ij^{th}$ 
entry 
% $\kappa_{ij}$ where

\begin{equation}
    \label{eq:qclt_covariance}
    \kappa_{ij} = \frac{p_i \wedge p_j - p_i p_j}{f(Q(p_i)) f(Q(p_j))}.
\end{equation}
\end{theorem}

@@

\begin{equation}
    \label{eq:qgp}
\hat{\boldsymbol{Q}}_n(\boldsymbol{p}) \sim N_K(\boldsymbol{Q}_{\theta}(\boldsymbol{p}), n^{-1} \boldsymbol{\mathcal{K}}_{\theta})
\end{equation}
Here $\theta$ is an unknown parameter vector to be estimated from the data. The 
covariance matrix $\boldsymbol{\mathcal{K}}_{\theta}$ has entries from the 
covariance function $\kappa_{\theta}(\cdot, \cdot)$ where 
\[
\kappa_{\theta}(p, p') = \frac{p\wedge p' - p p'}{f_{\theta}(Q_{\theta}(p)) f_{\theta}(Q_{\theta}(p'))}, \quad p, p' \in (0,1)
\]

@@

Take for instance the data 
$\boldsymbol{X} = \left(\textbf{1}, \Phi^{-1}(\boldsymbol{p})\right)$ and the 
parameter vector $\beta = (\mu, \sigma)$. Assuming the sample size $n$ is 
unknown and setting $\sigma^2/n = \gamma^2$, model (\ref{eq:norm_qgp}) then 
becomes
\[
    \hat{\boldsymbol{Q}}_n(\boldsymbol{p}) \sim N_K\left(X\beta, 
\gamma^2 \boldsymbol{\Psi}\right)
\]
In this model, one simplifying assumption may be to treat $\sigma$ and 
$\gamma^2$ separately and proceed to fit a standard linear regression model. 
All frequentist and Bayesian results of the linear regression model apply, 
including the existence of conditionally conjugate prior distributions. The 
positive constraint on $\sigma$ can also be dealt with without adding much 
complication (see \cite{gelman2013bayesian} pgs. 377-378). 
If, for a certain problem it is important to make inference on the unknown $n$, or $\sigma$ and 
$\gamma^2$ cannot treated as separate, then one may estimate the two parameters 
by assigning appropriate prior distributions to $\sigma$ and $n$ and reverting 
back to (\ref{eq:norm_qgp}). In section \ref{sec:simulation_analyses}, we 
analyze a normal QGP in a simulation study where we assign independent prior 
distributions to $\sigma$ and $n$, and $\sigma$ is treated as both a regression 
coefficient and as part of the variance.

@@

We define a modified version of the WD, the uniform 1-WD (UWD1) in 
(\ref{eq:pit_wass_dist}). Here we take $F_X$ to be the CDF of a continuous 
random variable $X$. For a different continuous random variable $\xi$ with CDF 
$F_{\xi}$, $F_X(\xi)$ is a random variable with support on $[0,1]$. We let 
$F_{X,\xi}$ be the CDF of the random variable $F_X(\xi)$. Then the measure in 
(\ref{eq:pit_wass_dist}) is a measure of how close $F_X(\xi)$ is the the CDF of 
a standard uniform distribution, noting that by the PIT, if 
$\xi \overset{D}{=} X$, $F_X(\xi)$ is the random variable of a standard uniform 
distribution. Multiplying the integral in (\ref{eq:pit_wass_dist}) by two 
ensures the measure takes values between 0 and 1 
\cite[]{645854} \jarad{I think the URL should be in the citation not here. Also, is this mentioned anywhere else so that we don't have to cite stackexchange?}
where a value near 0 means $\xi$ and $X$ are ``near'' each other.

@@

\subsubsection{Normal parameter estimation}
In this simulation study, we fit the ORD and IND models to quantiles estimated 
from independent samples from a normal distribution and compare parameter 
estimation with fits from the QGP model. Quantiles were simulated by first 
drawing a sample of size $n$ from a known distribution then estimating $K$ 
quantiles given probabilities $\{p_1, ..., p_K\}$. The ORD, IND, and QGP models 
were then fit to the quantiles where $F$ was set to be the CDF of a normal 
distribution. For each of 
$n \in \{50; 150; 500; 1{,}000; 5{,}000\}$ and 
% $K \in \{3,7,15,50\}$
$K = 23$, there 
were 500 simulation replicates. The data were simulated from a normal 
distribution with mean $\mu = 4$ and standard deviation $\sigma = 3.5$.
For each of QGP, ORD, and IND models, we assigned the same prior distributions 
to $\mu$ and $\sigma$. When $n$ is unknown, we also assigned it a prior 
distribution. The prior distributions were $\mu \sim N(5,7^2)$, 
$\sigma \sim N(0, 6^2) \mathds{1} \{\sigma > 0\}$, and
$n \sim N(0,3000^2)\mathds{1}\{n > 0\}$.
% \begin{align*}
%     \mu &\sim N(5,7^2) \\
%     \sigma &\sim N(0, 6^2) \mathds{1}\{\sigma > 0\}\\
%     n &\sim N(0,3000^2)\mathds{1}\{n > 0\}.
% \end{align*}
For the IND model the prior on the independent parameter 
$\sigma_{\rho}\mathds{1}\{n > 0\}$ from model (\ref{eq:ind_quantile}) is 
$1/\sigma_{\rho} \sim N(0, 3000^2)$, 
\jarad{Shouldn't this prior be strictly positive?}
which is similar to the prior on $n$ for 
the QGP and ORD models. For each fit, the HMC chain was run for 60,000 draws 
with the first 10,000 discarded as a burn-in.

@@

The top of figure \ref{fig:normal_cov_dists} shows the 90\% coverage of 
the posterior distribution credible intervals as $n$ increases for 
$\mu$, $\sigma$ and $n$ for five models. QGP-n and ORD-n models where $n$ is 
known are included along with QGP, ORD, and IND. 
The 90\% credible intervals of the 
parameters were calculated by computing the $0.05^{th}$ and $0.95^{th}$ 
quantiles from the posterior distribution samples. The coverage percentage is 
calculated as the percentage of the 500 replicates which the true parameter 
value was within the 90\% credible interval.
As expected, the nominal coverage for the QGP and ORD models is better than 
that of the IND model, and for the two models where $n$ is known the coverage 
is better than where it is unknown, particularly for lower values of 
$n$ and $K$. The coverage for the ORD models appears to be slightly better 
than for the QGP models though not by much, and the difference
decrases as $n$ increases. 
The superior performance of the ORD model is possibly because it
provides exact inference 
whereas the QGP model provides asymptotic inference.

\begin{figure}[hbt!]
%\begin{subfigure}{.465\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/normal_coverage.png}
  % \caption{}
  % \label{MLEDdet}
%\end{subfigure}\hfill % <-- "\hfill"
%\begin{subfigure}{.524\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/normal_dists.png}
  \centering
  \includegraphics[width=1\linewidth]{Images/normal_cover_dist.png}
  % \caption{}
  % \label{energydetPSK}
%\end{subfigure}
\caption{Posterior coverage (top) for models of $K = 23$ quantiles
calculated as the percentage of times the 
true parameter fell within the modeled 90\% credible interval over the 500 
replications. Coverage is faceted by the normal parameters $\mu$, $\sigma$,
and shown by increasing sample size 
($x$-axis). The five models QGP, ORD, QGP-n, ORD-n, and IND are colored as 
shown the legend. The horizontal line (black) is at the nominal 90\% level. 
Only QGP and ORD appear for inference for the parameter $n$ as they are the 
only two models which 
estimate an unknown $n$.
Distance between the true distribution and the estimated QM predictive 
distribution (bottom) averaged over the 500 replications. Distances include the 
UWD1, TV, and KLD for increasing sample 
size ($x$-axis).}
\label{fig:normal_cov_dists}
\end{figure}

@@

\begin{figure}[hbt!]
%\begin{subfigure}{.465\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/uk_cover50.png}
  % \caption{}
  % \label{MLEDdet}
%\end{subfigure}\hfill % <-- "\hfill"
%\begin{subfigure}{.532\linewidth}
  % \includegraphics[width=.4\linewidth]{Images/uk_cover95.png}
  % \caption{}
  % \label{energydetPSK}
%\end{subfigure}
\centering
\includegraphics[width=.9\linewidth]{Images/uk_cover_dist.png}
\caption{
(top) Percent coverage of the true quantile values for select quantiles for 
500 simulated replicates of sample quantiles averaged over all $K = 23$
quantiles faceted by the true EV, La, and normal mixture distributions.
The plots shows percent coverage for the 95\% credible intervals. The models 
included are QGP, ORD, and IND. The vertical bar (black) shows the nominal 
coverage level.
(bottom) Distance between the true distribution and the QM estimated 
distribution 
averaged over 500 simulation replicates and measured by KLD, TV and UWD1. 
Plots are faceted by distribution with the distributions being 
EV, La, and MIX. 
Lines are colored and shaped by QM method, and are drawn by increasing sample 
size $n$.}
\label{fig:uk_cover}
\end{figure}

The bottom of \ref{fig:uk_cover} shows the UWD1, TV, and KLD distances between 
QM and true distributions averaged over 500 simulation replicates for the 
five QM methods. In the UWD1 plot, there appears to be little or no difference
in performance between the QGP, ORD, IND, and SPL fits, but each of these
outperforms the KDE fits. For TV, the QGP, ORD, and SPL perform similarly, 
though the QGP does the best for the MIX distribution.
And for KLD, the QGP and ORD perform the best for lower values of $n$, but as
$n$ increases, SPL appears to perform the best. Additional plots and results
from these analyses are found in the supplementary material.
